Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-01 Thesis/chapter/031-theory-calculations.tex
experiment fertig druebergelesen
post-emma table
start incorporate post-emma into theory

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%\href
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
%\td{The goal of machine learning is to ???}
%
%\begin{itemize}
%	\item \td{let GPT-3 write}
%	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
%	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
%	\item 
%		\href
%		{https://doi.org/10.1177\%2F1352458520978648}
%		{Machine and deep learning in MS research are just powerful statistics – No}
%\end{itemize}
%
%\td{
%\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
%In principle both \gls{ml} and statistics use math to get information out of data. 
%AI might use machine learning to create "intelligent" acting (playing a game or driving a  car). 
\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This allows the statistician to better study how a change in the input variable can be 
directly affected by the output variable.\cite{gontcharov2019}
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
%}
%What is statistics, though, and what seperates it from \gls{ml}? 
More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of 
finding mathematical models to describe the data 
whereas (classical) statistics is the domain of representing the data. 
\td{talk about statistics, then the difference to Ml} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\Gls{pso} also uses a starting population of particles where each experiment (particle) 
is represented by its independent and dependent variables. 
It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995}.
Each particle has an associated position and velocity. 
Every movement across the search space is 
additionally to a stochastic term
%stochastic and 
influenced by its particle velocity and position as well as its and the swarm's best visited position.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%\href
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
What is \gls{ml}? Some might argue that \gls{ml} is just overglorified statistics, but that's not the case. 
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different. 
%\td{The goal of machine learning is to ???}
%
%\begin{itemize}
%	\item \td{let GPT-3 write}
%	\item check out links at \url{https://yewtu.be/watch?v=PqbB07n\_uQ4}
%	\item see pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
%	\item 
%		\href
%		{https://doi.org/10.1177\%2F1352458520978648}
%		{Machine and deep learning in MS research are just powerful statistics – No}
%\end{itemize}
%
%\td{
%\url{https://stats.stackexchange.com/questions/5026/what-is-the-difference-between-data-mining-statistics-machine-learning-and-ai}
%In principle both \gls{ml} and statistics use math to get information out of data. 
%AI might use machine learning to create "intelligent" acting (playing a game or driving a  car). 
\Gls{ml} tries to predict unseen data points and statistics is a subfield of maths 
which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This allows the statistician to better study how a change in the input variable can be 
directly affected by the output variable.\cite{gontcharov2019}
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
%}
%What is statistics, though, and what seperates it from \gls{ml}? 
More precisely, mathematical statistics (stochastic)\cite{haertler2014statistisch} is the subject of of 
finding mathematical models to describe the data 
whereas (classical) statistics is the domain of representing the data. 
\td{talk about statistics, then the difference to Ml} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\td{if i want to learn about support vector machine, read chapter 4,7,8 from "Learning from Data" by Cherkassky\cite{cherkassky1998learning} (TUBib 726-1998)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\Gls{pso} also uses a starting population of particles where each experiment (particle) 
is represented by its independent and dependent variables. 
It was originally inspired by the behaviour of bird flocks and fish schools\cite{Kennedy1995,villanova2010function}.
%"PSO is a population based heuristic inspired by the flocking behavior of birds. 
%To simulate the behavior of a swarm, each bird (or particle) is allowed to fly towards the optimum solution."\cite{villanova2010function}
Each particle has an associated position and velocity. 
Every movement across the search space is 
additionally to a stochastic term
%stochastic and 
influenced by its particle velocity and position as well as its and the swarm's best visited position.

@@

%%% FEATURE SELECTION 
% https://stats.stackexchange.com/questions/39243/how-does-one-interpret-svm-feature-weights
% gene (feature) selection with SVM https://link.springer.com/content/pdf/10.1023/A:1012487302797.pdf
% Intro to feature selection https://axon.cs.byu.edu/Dan/778/papers/Feature%20Selection/guyon2.pdf

\td{statistical methods to bewerten a model are: cross validation, leave-one-out validation ( special case of cross validation), correlation coefficient for linear fits, mean square error. methods to fit data are: lin reg, polynomial regression, ridge regression, KRR, SVM and?}

### 2023-02-01 Thesis/chapter/063-discussion.tex
finish EMMA coeff analysis
start incorporate post-emma into theory

>>>>

\td{two main problems: 1. too many input variables; 2. too many output varibales; at2: as some input variables were also output variables, MARS couldnt find correct BFs. This could be used though: use input var also as output var if you think they are inportant, this way they will be more likely to be choosen in basis function}

\td{The goal of introducing \gls{ml} to this project was to apply and delve/vertiefen into subject which I've been studying during my undergrad courses. This seemed like the perfect opputrunity. And indeed I learned a lot. Even if only although \gls{ml} is a hot topic at the moment, it can not solve every problem. Two important things have I learned regarding \gls{ml}: 
1.) The methods bringen sich nix if one doesn't know how to apply them which directly leads into my second erkenntnis
2.) If one wants to use a tool, one should know how to use it and its innerlichkeiten in order to use it well.
The second point is not the best comparison because one doesn't need to know how a light switch works in order to use it effectively use it.}
